Transfer report

### 2019-06-19 Report/final-results.Rmd
Updates final results

df_wide_errors$block34 <- (df_wide_errors$block3-df_wide_errors$block4)/(df_wide_errors$block3+df_wide_errors$block4)
df_wide_distance$block34 <- (df_wide_distance$block3-df_wide_distance$block4)/(df_wide_distance$block3+df_wide_distance$block4)

@@

We also observed significant differences between conditions in pointing performance at the end of the first phase, `r apa_print(aov_point_phase1)$full_result$learning_condition`.  Specifically, participants in the real-world learning group  (`r m_sd_report(only_conditions(point_data_1, "Real")$abs_error)`) performed significantly better compared to both the immersive VR group (`r m_sd_report(only_conditions(point_data_1, "Treadmill VR")$abs_error)`), `r t_test_effect(abs_error ~ learning.condition, only_conditions(point_data_1, c('Real', 'Treadmill VR')))`, and the desktop group (`r m_sd_report(only_conditions(point_data_1, "Desktop")$abs_error)`), `r t_test_effect(abs_error ~ learning.condition, only_conditions(point_data_1, c('Real', 'Desktop')))`. Overall, these findings suggested that participants learned the building the best as a result of real-world navigation, followed by the immersive condition, with the desktop condition showing the slowest acquisition.

@@

@@

As an additional assay of transfer, we wished to determine whether learning post modality switch was faster in the group that had been exposed to the real-world in the learning blocks compared to the VR groups. Comparing walked distance and visitation errors across between blocks 4 and 6 by running repeated measures ANOVA, we found a significant effect of learning condition on distance,`r apa_print(ez_fit_distance$aov)$full_result$learning_condition` and visitation errors `r apa_print(ez_fit_errors$aov)$full_result$learning_condition`. We also wound significant interaction effect between learning condition and block for both distance `r apa_print(ez_fit_distance$aov)$full_result$learning_condition` and visitation errors `r apa_print(ez_fit_errors$aov)$full_result$learning_condition`.

@@

```{r}
kable(tukey_report_table(TukeyHSD(aov(min_norm_distance ~ condition, only_blocks(walk_all, c(6))))))
```

>>>>

df_wide_errors$block34 <- (df_wide_errors$block3-df_wide_errors$block4)/(df_wide_errors$block3+df_wide_errors$block4)
df_wide_errors$block34[is.na(df_wide_errors$block34)] <- 0 #fixes case where person scores 0 in block 3 and 4 and so we have
df_wide_distance$block34 <- (df_wide_distance$block3-df_wide_distance$block4)/(df_wide_distance$block3+df_wide_distance$block4)

@@

We also observed significant differences between conditions in pointing performance at the end of the first phase, `r apa_print(aov_point_phase1)$full_result$learning_condition`.  Specifically, participants in the real-world learning group  (`r m_sd_report(only_conditions(point_data_1, "Real")$abs_error)`) performed significantly better compared to both the immersive VR group (`r m_sd_report(only_conditions(point_data_1, "Treadmill VR")$abs_error)`), `r t_test_effect(abs_error ~ learning.condition, only_conditions(point_data_1, c('Real', 'Treadmill VR')))`, and the desktop group (`r m_sd_report(only_conditions(point_data_1, "Desktop")$abs_error)`), `r t_test_effect(abs_error ~ learning.condition, only_conditions(point_data_1, c('Real', 'Desktop')))`, but no difference between VR and desktop (`r t_test_effect(abs_error ~ learning.condition, only_conditions(point_data_1, c('Treadmill VR', 'Desktop')))`). Overall, these findings suggested that participants learned the building the best as a result of real-world navigation, followed by the immersive condition, with the desktop condition showing the slowest acquisition.

@@

```{r}
### graphs
ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = min_norm_distance, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average normalised trial distance") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")

ggplot(only_blocks(sub_walk_all_factor, 3:4), aes(x = graph.exp_block_id, y = errors, fill = graph.exp_block_id)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average visitation errors") + xlab("Learning condition") + 
  scale_fill_manual(values=estimote_pal,"Block") + guides(fill=F) +
  facet_wrap(~graph.learning.condition, strip.position = "bottom", scales = "free_x") + 
  theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside")

@@

As an additional assay of transfer, we wished to determine whether learning post modality switch was faster in the group that had been exposed to the real-world in the learning blocks compared to the VR groups. Comparing walked distance and visitation errors across between blocks 4 and 6 by running repeated measures ANOVA, we found a significant effect of learning condition on distance,`r apa_print(ez_fit_distance$aov)$full_result$learning_condition` and visitation errors `r apa_print(ez_fit_errors$aov)$full_result$learning_condition`. We also wound significant interaction effect between learning condition and block for both distance `r apa_print(ez_fit_distance$aov)$full_result$learning_condition_exp_block_id` and visitation errors `r apa_print(ez_fit_errors$aov)$full_result$learning_condition_exp_block_id`.

@@

```{r}
kable(tukey_report_table(TukeyHSD(aov(min_norm_distance ~ condition, only_blocks(walk_all, c(6))))))

kable(tukey_report_table(TukeyHSD(aov(errors ~ condition, only_blocks(walk_all, c(6))))))
```
